
# **OSATS**

OSATS is a evaluation instrument that consists of a grading scale and a checklist. Used to grade performance in surgical training tasks. Grading is done by expert surgeons, often from video recordings of the training task.

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
library(knitr)
```
Load data
```{r}
df.osats <- read_excel('data/surgical_metrics.xlsx', sheet='scale_OSATS')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.osats[,c("Author", "Year", "Study", "Journal", "Note")])
```
## Results
Run meta-analysis
```{r}
m.osats <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.osats,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="OSATS in Surgery")
```
```{r}
summary(m.osats)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.osats,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="OSATS in Surgery")
#dev.print(pdf, "figures/forest_OSATS.pdf", width=8, height=8)
```

## Discussion
Not many papers that focused on tool accelerations. Jerk (third derivative of position, derivative of acceleration) is much more popular.

Results show that experts are consistently evaluated to have performed the tasks better than novices. All studies show significant differences between novices and experts.