
# **Tool Velocity**

Tool velocity/speed measures how fast the surgical tool or tools are moving.

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.toolvelocity <- read_excel('data/surgical_metrics.xlsx', sheet='tool_velocity')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.toolvelocity[,c("Author", "Year", "Study", "Journal", "Note")])
```
## Results
Run meta-analysis
```{r}
m.toolvelocity <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.toolvelocity,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Tool velocity in Surgery")
```
```{r}
summary(m.toolvelocity)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.toolvelocity,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Tool velocity in Surgery")
#dev.print(pdf, "figures/forest_toolvelocity.pdf", width=8, height=8)
```

## Discussion
Velocity and related metrics like acceleration are also semi-popular methods. Based on the reviewed studies, the results vary a lot. This indicates that while novices spend more time with the task (see task time results) and move the tools for longer paths (see tool path length results), the velocity of the movements do not differ from experts consistently. Or at least the results depend on surgical technique and task.