

# **Task Time**

Task time is the time taken to complete a task. Task can be short like a single knot or some longer complex task.

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
library(knitr)
library(lme4)
```
Load data
```{r}
df.time <- read_excel('data/surgical_metrics.xlsx', sheet='task_time')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.time[,c("Author", "Year", "Study", "Journal", "Note")])
```

## Results
```{r}
m.time <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.time,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Time to completion in Surgery")
```
```{r}
summary(m.time)
```
Plot forest
```{r, fig.width = 10, fig.height=9}
forest.meta(m.time,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Time to completion in Surgery")
#dev.print(pdf, "figures/forest_time.pdf", width=10, height=10)


```
### Meta-regression (testing)

With enough results, we can do regression analysis to compare e.g. how the effect sizes differed between surgical techniques.

First, plot by surgical technique (red labels show the number of studies):

```{r}
n_obs <- function(x){
  return(c(y=0, label=length(x)))
}
ggplot(df.time, aes(x=Technique, y=SMD)) + geom_boxplot() + stat_summary(fun.data = n_obs, colour = "red", size = 5, geom = "text")
```


Fit linear model with Technique as explanatory variable. Microsurgery effect size is used as baseline (intercept).

```{r}
df.time$Technique <- as.factor(df.time$Technique)
df.time <- within(df.time, Technique <- relevel(Technique, ref="Microsurgery"))
lm.time <- lm(SMD ~ Technique, data=df.time)
summary(lm.time)
```


## Discussion

Time to completion is by far the most often reported metric. It is often reported even when it is not the main focus of the study.




