# **Tool Idle Time**

Tool idle time measures how long the tools were not being used, either as time or as fraction of the complete task time.

Idle time (IT) can be measured in different ways, but the common theme is that we compare the time when tools are actively used ($T_a$) with the time when they are not actively being used $T_{na}$.

$$
IT = \frac{T_{na}}{T_a + T_{na}} = \frac{T_{na}}{T_{total}}
$$

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.toolidle <- read_excel('data/surgical_metrics.xlsx', sheet='tool_idle')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.toolidle[,c("Author", "Year", "Study", "Journal", "Note")])
```
## Results
Run meta-analysis
```{r}
m.toolidle <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.toolidle,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Idle time in Surgery")
```
```{r}
summary(m.toolidle)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.toolidle,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Idle time in Surgery")
#dev.print(pdf, "figures/forest_toolidle.pdf", width=8, height=8)
```

## Discussion
Not many papers that focused on idle time. However, with one exception it seems to imply that novices have more idle time than experts. The one clear exception, Perez-Escamirosa et al., measured idle time by the time when tools were in contact with the training pad. This method may have missed a lot of instances that would have been counted as idle time in other studies.