# **Task-Evoked Pupil Dilation**

Pupil size measures cognitive workload, stress, and million other things.

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.pupil <- read_excel('data/surgical_metrics.xlsx', sheet='pupil_dilation')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.pupil[,c("Author", "Year", "Study", "Journal")])
```
## Results
Run meta-analysis
```{r}
m.pupil <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.pupil,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Pupil dilation in Surgery")
```
```{r}
summary(m.pupil)
```
Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.pupil,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Pupil dilation in Surgery")
dev.print(pdf, "figures/forest_pupil.pdf", width=8, height=8)
```


## Discussion
Prior research indicates that higher stress/cognitive workload -> larger pupil size. This is seen in most studies. In Bednarik et al. (2018), the effect is reversed. For that study, I picked needle piercing segment (because it was quaranteed to have un-interrupted visual contact from the participant). It can be that experts focused more on this, and had larger cognitive workload and pupil dilations.

Not that many studies that have measured pupil dilations and compared surgical novices and experts directly. Some used measures like ICA or Entropy (not included here). Pupil dilations used in other fields more often.