
# **Tool Force**

Tool force is the force the surgeon uses when they e.g. grasp something using the surgical tools. Usually measured with force-sensors attached to the instruments. Perez-Escamirosa measured force with sensors attached to the pad where the task was completed.

## Studies
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.force <- read_excel('data/surgical_metrics.xlsx', sheet='tool_force')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.force[,c("Author", "Year", "Study", "Journal", "Note")])
```
## Results
Run meta-analysis
```{r}
m.force <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.force,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Force use in Surgery")
```
```{r}
summary(m.force)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.force,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Force use in Surgery")
#dev.print(pdf, "figures/forest_toolforce.pdf", width=8, height=8)
```

## Discussion
Forces are analyzed somewhat commonly, but often not between novices and experts, but instead within tasks, or tools, or skill groups.

Nonetheless, the results show that novices use larger forces when completing a task. The one exception is Prasad, whose study showed strong negative effect indicating that experts used larger forces. **TBD: investigate why**.