
# **Tool Movements**

Number of tool movements made during the task. Note: This includes studies that reported all sub-movements and studies that focused on some sub-section of all movements. For example, Koskinen et al. studied only grasping with the surgical tool.

## Studies

```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.toolmvt <- read_excel('data/surgical_metrics.xlsx', sheet='tool_movements')
```
Print studies
```{r echo = FALSE, results = 'asis'}
kable(df.toolmvt[,c("Author", "Year", "Study", "Journal", "Note")])
```
## Results
Run meta-analysis
```{r}
m.toolmvt <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.toolmvt,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Tool movements in Surgery")
```
```{r}
summary(m.toolmvt)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.toolmvt,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Tool movements in Surgery")
#dev.print(pdf, "figures/forest_toolmvt.pdf", width=8, height=8)
```

## Discussion
Tool movements are perhaps the second most often reported metric. Different papers measure, analyze and report them differently. Often connected to "movement efficiency".

This is also a consistent metric. With the exception of three studies, the studies showed that novices have significantly more movements than experts.
