

# Task time

Task time is the time taken to complete a task. Task can be short like a single knot or some longer complex task.

## Results
```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.time <- read_excel('data/surgical_metrics.xlsx', sheet='task_time')
```
Show data. Data has time to completion results for novices and experts from different studies. Original time (Mn and Me) given in seconds.
```{r}
head(df.time, 1)
```

```{r}
m.time <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.time,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Time to completion in Surgery")
```
```{r}
summary(m.time)
```
Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.time,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Time to completion in Surgery")
dev.print(pdf, "figures/forest_time.pdf", width=8, height=8)


```
## Discussion

Time to completion is by far the most often reported metric. It is often reported even when it is not the main focus of the study.




