
# Tool movements

Number of tool movements made during the task. Note: I have included here the grasp results from our paper (and other studies that analyzed only one type of action/movement)

## Results

```{r, results='hide', message=FALSE, echo=FALSE, warning=FALSE}
library(meta)
library(esc)
library(tidyverse)
library(stargazer)
library(readxl)
```
Load data
```{r}
df.toolmvt <- read_excel('data/surgical_metrics.xlsx', sheet='tool_movements')
```
Run meta-analysis
```{r}
m.toolmvt <- metagen(TE=g,
                 seTE=SDg,
                 studlab=Author,
                 data=df.toolmvt,
                 sm="SMD",
                 fixed=FALSE,
                 random=TRUE,
                 method.tau="REML",
                 hakn=TRUE,
                 title="Tool movements in Surgery")
```
```{r}
summary(m.toolmvt)
```

Plot forest
```{r, fig.width = 10, fig.height=5}
forest.meta(m.toolmvt,sortvar=g, prediction=TRUE, prin.tau2=TRUE, title="Tool movements in Surgery")
dev.print(pdf, "figures/forest_toolmvt.pdf", width=8, height=8)
```

## Discussion
Tool movements are perhaps the second most often reported metric. Different papers measure, analyze and report them differently. Often connected to "movement efficiency".
